MSPMS Report

### 2024-05-31 inst/rmarkdown/templates/mspms_report/skeleton/skeleton.Rmd
major changes

```{r setup, include=FALSE}
library(dplyr)
ggplot2::theme_set(ggplot2::theme_minimal())
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
```

@@

```{r}
# The standard mspms data processing pipeline is used here. 
mspms = mspms::mspms(prepared_data,design_matrix)
```

# Overview 
```{r}
mspms::plot_pca(mspms)
```

@@

```{r}
mspms::plot_heatmap(mspms)
```

@@

```{r}
t1 = mspms::mspms_anova(mspms) %>% 
  dplyr::arrange(p.adj)

@@

```{r}
t2 = log2fc_t_test(mspms) %>% 
  dplyr::arrange(p.adj)

@@

```{r}
print(mspms::plot_all_icelogos(mspms))
```

>>>>

```{r setup, include=FALSE}
library(dplyr)
ggplot2::theme_set(ggplot2::theme_bw())
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
```

@@

```{r}
# The standard mspms data processing pipeline is used here. 
mspms_data = mspms::mspms(prepared_data,design_matrix)
```

# Overview 
```{r}
mspms::plot_pca(mspms_data)
```

@@

```{r,fig.height = 8, fig.width = 10}
mspms::plot_heatmap(mspms_data)
```

@@

```{r}
t1 = mspms::mspms_anova(mspms_data) %>% 
  dplyr::arrange(p.adj)

@@

```{r}
t2 = log2fc_t_test(mspms_data) %>% 
  dplyr::arrange(p.adj)

@@

```{r,fig.height = 10, fig.width = 6}
print(mspms::plot_all_icelogos(mspms_data))
```
